\documentclass[a4paper, 12pt]{article}

% \newenvironment{ltable}
%   {\begin{landscape}}
%   {\end{landscape}}
% \DeclareDelayedFloatFlavour{ltable}{table}

% \usepackage{pdflscape}

\usepackage{subcaption}
\captionsetup[sub]{font=footnotesize, labelfont={bf,sf}} % 8pt for subcaptions

%% AMS mathematics packages - they contain many useful fonts and symbols.
\usepackage{amsmath, amsfonts, amssymb, amsthm, mathtools}
\usepackage{float}
% \floatplacement{figure}{H}
% \floatplacement{table}{H}

\usepackage{graphicx}

\usepackage{bbm}
\usepackage{physics}

\usepackage{setspace}
\usepackage{natbib}
\usepackage{tabularx}

\usepackage{tabularray}
\usepackage{codehigh}
\usepackage[normalem]{ulem}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}

\usepackage[paper=a4paper, left=20mm, right=20mm, top=20mm, bottom=20mm]{geometry}

\usepackage{url}
\sloppy
\def\UrlBreaks{\do\/\do-}
\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}

\usepackage[at]{easylist}

% \usepackage{newtxtext} % Use Times Roman font
% \usepackage{newtxmath} % Use Times Roman font
% \usepackage[T1]{fontenc}
\usepackage{newpxtext, newpxmath}

% \usepackage[ipa]{luatexja-preset}

\newcommand{\E}{\mathbb{E}}
\newcommand{\suminf}[1]{\sum_{#1=0}^\infty}
\theoremstyle{definition*}
\newtheorem*{definition*}{Definition}

\begin{document}
\begin{titlepage}
\title{TITLE\thanks{COMMENTS. All remaining errors are my own.}}
\author{Candidate Number: 61980}
\date{XX May 2026 \vskip \baselineskip Word Count: XXXX}
\maketitle
\begin{abstract}
\noindent Abstract here. \\
\vspace{0in}\\
\noindent\textbf{Keywords:} Keyword 1, keyword 2, keyword 3\\
\vspace{0in}\\
\noindent\textbf{JEL Codes:} J63, J64, E24\\

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

\pagenumbering{roman}
\tableofcontents
\listoffigures
\listoftables

\pagebreak \newpage

\pagenumbering{arabic}
\onehalfspacing

\section{Introduction}

The energy crisis in 2022 has led to a surge in natural gas price, which has in turn caused a significant increase in inflation in the UK.
Whereas the natural gas price shock was transitory, the inflation response was lagged and persistent: the peak of the inflation response occurred a few months later than that of the natural gas price, and the inflation rate remained elevated for a long time after the natural gas price returned to normal. \textcolor{blue}{TODO: present observations!}

The standard New Keynesian model for a small open economy which imports energy as a factor of production at an exogenous price (hereafter ``the baseline model'') fails to replicate this hump-shaped and persistent response of inflation to the energy price shock.

I extend the baseline model in two following ways to replicate a hump-shaped and persistent inflation response to the energy price shock.
First, I introduce production networks with an upstream industry that utilises imported energy and labour to produce intermediate goods and a downstream industry using the intermediate goods and labour to produce final goods that are consumed by households.
There is a single labour market for both industries, where workers move freely between the two industries.
Consequently, the wage is identical across the two industries in the equilibrium.
An important feature of this model's production network is that the downstream industry is myopic in its pricing decisions (see \cite{minton2023delayed}).
While non-myopic Calvo-pricing firms incorporate full information about the expected future marginal cost into their reset price calculations, myopic firms discount the future expected marginal cost and hence put more weight on the current marginal cost when setting their prices.
The myopia of the downstream industry corresponds to the difficulty, particularly for downstream firms, to perfectly foresee the future path of energy price, compared to the upstream industry. \textcolor{blue}{TODO: more details here.}

Second, I introduce real wage rigidity in the labour market, which represents the friction in the labour market such as fixed contracts, negotiation costs, and separation/hiring costs.

The rest of the paper is organised as follows.
The following subsection explores the literature.
In Section \ref{sec:model}, I describe the baseline model and its extensions, as well as calibrate the model parameters for the simulation.
In Section \ref{sec:results_and_discussion}, I present the simulation results and evaluate them by conducting further sensitivity analysis.
Finally, the paper concludes in Section \ref{sec:conclusion}.

Observation:
\begin{easylist}[itemize]
  @ Hump shaped response of inflation to oil price shock.
  @ Inflation rises after a lag, then falls with some persistence
\end{easylist}


\begin{easylist}[itemize]
  @ Production networks
    @@ Upstream industry: energy + labour -> intermediate goods
    @@ Downstream industry: intermediate goods + labour -> final goods
    @@ Myopic: can't perfectly foresee the future path of oil price, so they set prices (partly) based on current cost
  @ Real wage rigidity
    @@ representing the friction in the labour market, such as fixed contracts, negotiation costs, and separation/hiring costs
  @ Sensitivity analysis
\end{easylist}

\subsection{Literature}

\cite{gagliardone2025oil} explores AAA.

\cite{gomellini2025inflation} explores BBB.


\begin{easylist}[itemize]
  \ListProperties(Style=\color{blue})
  @ Production networks
  @ Real wage rigidity
  @ Oil shock \url{https://www.nber.org/papers/w13368}
\end{easylist}

\section{The Model}\label{sec:model}

\textcolor{blue}{Plan: \url{https://claude.ai/chat/72a44bc1-0451-4698-a8c1-b9c165442122}}


% \subsection{The Baseline Model}
% 10 endogenous variables and 10 equations.

% Endogenous variables: $\pi_t, P_t, P_t^*, x_t, w_t, Y_t, L_t, s_t, i_t, C_t$
% \begin{align}
%   i_t   &= \phi i_{t-1} + (1-\phi)(\chi_pi \pi_t + \chi_y Y_t) & \text{Taylor rule} \\
%   C_t   &= \E_t C_{t+1} - \sigma(i_t - E_t \pi_{t+1}) & \text{Euler equation} \\
%   w_t   &= \frac{1}{\sigma}Y_t + \frac{1}{\psi}L_t & \text{Labour supply} \\
%   P_t   &= \theta P_{t-1} + (1-\theta)P_t^* & \text{Calvo pricing} \\
%   P_t^* &= \beta \theta P_{t+1}^* + (1-\beta \theta)MC_t & \text{Reset price} \\
%   x_t   &= X_t - P_t & \text{Real marginal cost} \\
%   \pi_t &= P_t - P_{t-1} & \text{Inflation} \\
%   x_t   &= w_t + \alpha s_t & \text{Real marginal cost} \\
%   Y_t   &= L_t - \alpha s_t & \text{Aggregate production function} \\
%   s_t   &= \rho s_{t-1} + \u_t & \text{Exogenous process for terms of trade}
% \end{align}

% \subsection{Extensions: Production Networks and Real Wage Rigidity}
\subsection{Economic Environment and Terms-of-Trade Shock}
Consider a small open economy with two industrial sectors that imports a quantity $Z_t$ of energy from the rest of the world.
Assume the economy does not produce energy domestically, and its domestic demand for energy does not affect the global energy price.
There is also a homogenous internationally tradable good that the economy can produce and export.
Assume without loss of generality that the domestic economy can produce $E_t$ units of this traded good using $E_t$ units of domestic labour, and the market for the traded good is perfectly competitive.
This implies that the domestic-currency price of the traded good is equal to the nominal wage $W_t$, the nominal marginal cost of production.
Define the unit price of energy imports in domestic currency to be $S_t$, and denote the relative price of imports to exports (i.e., the terms of trade) as $s_t = S_t / W_t$.
The small open economy takes this terms of trade $s_t$ as given, and shocks to $s_t$ represent energy price shocks in the analysis.

Assume that the terms of trade $s_t$ follows an exogenous AR(1) process.
Let $\hat s_t$ denote the log-deviation of $s_t$ from its steady state value $\bar s$ which is normalised to one without loss of generality, so $\hat s_t$ follows
\begin{equation}\label{eq:tot_process}
  \hat s_t = \rho \hat s_{t-1} + u_t,
\end{equation}
where $u_t$ is a zero-mean i.i.d. shock to the terms of trade, and $\rho$ measures the persistence of the exogenous shock.

All goods are perishable, and the model does not have financial assets to be traded internationally, so net exports must be zero in the balance-of-payments equilibrium.
Mathematically, this means $W_tE_t = S_tZ_t$, or equivalently,
\begin{equation}\label{eq:balance_of_payments}
  E_t = s_tZ_t.
\end{equation}

\subsection{Production Network}
Apart from the production of tradable goods (which utilises $E_t$ units of labour to produce the same quantity of the tradable goods), the economy entails a production network of domestic consumption goods, which consists of upstream and downstream industries.
Both industries use domestic labour as an input, which does not require any industry-specific skills, and the workers are completely mobile between the two industries, so that the wage is identical across the two industries in the equilibrium.

In the upstream industry, there is a continuum of firms $j \in [0,1]$ that uses imported energy and domestic labour to produce differentiated intermediate goods, which will be used as inputs by the downstream industry.
The production of the upstream industry firm $j$ is described by the following Leontief production function:
\begin{equation}
  Q_t(j) = \min\left\{\frac{Z_t(j)}{\alpha^U}, \frac{N^U_t(j)}{1 - \alpha^U}\right\},
\end{equation}
where $Q_t(j)$ denotes the output of firm $j$ in the upstream industry, $Z_t(j)$ and $N^U_t(j)$ denote the usage of energy and labour by firm $j$ as inputs, and the parameter $\alpha^U \in (0,1)$ is the share of energy in the production function.\footnote{I put a superscript $U$ ($D$) to indicate that a variable is about the upstream (downstream) industry.}
The production function is in Leontief form, which implies that there is no substitutability between energy and labour in producing the intermediate goods.
The production cost is composed of the cost of labour and energy, whose nominal prices are $W_t$ and $S_t$, respectively.
As the upstream industry firm minimises its production cost, energy and labour are used in fixed proportions:
\begin{equation}
  Z_t(j) = \alpha^U Q_t(j), \quad N^U_t(j) = (1 - \alpha^U)Q_t(j).
\end{equation}
The nominal marginal cost $X^U_t$ of producing one unit of intermediate good is constant across firms in the upstream industry and is given by
\begin{equation}\label{eq:nmcU}
  X^U_t = \alpha^U S_t + (1 - \alpha^U)W_t = (1 - \alpha^U + \alpha^U s_t)W_t.
\end{equation}
It follows that the real marginal cost $x^U_t = X^U_t / P^U_t$ is
\begin{equation}
  x^U_t = \left(1 - \alpha^U + \alpha^Us_t\right)\cdot\frac{W_t}{P^D_t}\cdot\frac{P^D_t}{P^U_t} = (1 - \alpha^U + \alpha^U s_t)\cdot w_t\cdot\frac{P^D_t}{P^U_t},
\end{equation}
where $w_t = W_t / P^D_t$ is the real wage.\footnote{Whereas measuring the real term of the upstream marginal cost by the price of intermediate goods $P^U_t$, I measure wage, which is constant across both industries, by the price of final consumption goods $P^D_t$.}
Since $\bar s = 1$ in steady state, the parameter $\alpha^U$ can be interpreted as the steady-state energy share of the upstream industry firm's production costs.
The basket of differentiated intermediate goods is aggregated into a composite intermediate good using a CES aggregator:
\begin{equation}
  Q_t = \left(\int_0^1 Q_t(j)^{\frac{\varepsilon - 1}{\varepsilon}} dj\right)^{\frac{\varepsilon}{\varepsilon - 1}}
\end{equation}
which is supplied to the downstream industry to be used in the production of consumption goods.
Here, $\varepsilon$ is the elasticity of substitution within the upstream industry intermediate goods.\footnote{For simplicity, the model assumes the elasticity of substitution is the same for both upstream and downstream industries. I conduct sensitivity analysis on this assumption in Section \ref{subsec:sensitivity_analysis} to show how results would change if it differs between the two industries.}

In the downstream industry, there is a continuum of firms $i \in [0,1]$ that uses the composite intermediate goods produced by the upstream industry as well as domestic labour to produce differentiated final goods, which are consumed by households.
The production of the downstream industry firm $i$ is also in Leontief form:
\begin{equation}
  Y_t(i) = \min\left\{\frac{M_t(i)}{\alpha^D}, \frac{N^D_t(i)}{1 - \alpha^D}\right\},
\end{equation}
where $Y_t(i)$ denotes the output of firm $i$ in the downstream industry, $M_t(i)$ and $N^D_t(i)$ denote the usage of intermediate goods composite and labour by firm $i$ as inputs, and the parameter $\alpha^D \in (0,1)$ is the share of intermediate goods composite in the production function.\footnote{$\alpha^D$ can be interpreted as the $(D, U)$-element of the input-output matrix in a more generalised production network model.}
Similarly to the production of the upstream industry, the production cost minimisation implies that intermediate goods and labour are used in fixed proportions:
\begin{equation}
  M_t(i) = \alpha^D Y_t(i), \quad N^D_t(i) = (1 - \alpha^D)Y_t(i).
\end{equation}
The nominal marginal cost $X^D_t$ of producing one unit of the final consumption good is
\begin{equation}
  X^D_t = \alpha^D P^U_t + (1 - \alpha^D)W_t,
\end{equation}
and the real marginal cost $x^D_t = X^D_t / P^D_t$ is
\begin{equation}\label{eq:rmcD}
  x^D_t = \left(1 - \alpha^D + \alpha^D\frac{P^U_t}{W_t}\right)\frac{W_t}{P^D_t} = \left(1 - \alpha^D + \alpha^D\frac{P^U_t}{W_t}\right)w_t.
\end{equation}

Domestic households consume the CES aggregated basket of differentiated final goods:
\begin{equation}
  C_t = \left(\int_0^1 C_t(i)^{\frac{\varepsilon - 1}{\varepsilon}} di\right)^{\frac{\varepsilon}{\varepsilon - 1}},
\end{equation}
where $C_t(i) = Y_t(i)$ holds in the equilibrium for all $i$ as the market clears.
Solving the household's utility maximisation problem under the budget constraint yields the demand for each differentiated final good $i$: \textcolor{blue}{SHOULD I SOLVE EXPLICITLY?}
\begin{equation}\label{eq:demand_final}
  Y_t(i) = \left(\frac{P^D_t(i)}{P^D_t}\right)^{-\varepsilon}Y_t,
\end{equation}
where
\begin{equation}
  Y_t = \left(\int_0^1Y_t(i)^{\frac{\varepsilon - 1}{\varepsilon}} di\right)^{\frac{\varepsilon}{\varepsilon - 1}}, \quad P^D_t = \left(\int_0^1 P^D_t(i)^{1-\varepsilon} di\right)^{\frac{1}{1-\varepsilon}}.
\end{equation}
Similarly, solutions to the downstream industry's cost minimisation problem yield the demand for each intermediate good $j$ by the downstream industry:
\begin{equation}\label{eq:demand_intermediate}
  M_t(j) = \left(\frac{P^U_t(j)}{P^U_t}\right)^{-\varepsilon}M_t,
\end{equation}
where $M_t = \int_0^1M_t(i)di$ is the downstream industry's aggregate demand for the intermediate goods basket.
In the equilibrium, the market for intermediate goods clears for each differentiated intermediate good $j$, so $M_t(j) = Q_t(j)$ for all $j$.

Since net exports are zero and there is no investment or government expenditure in the model, aggregate output of the downstream industry $Y_t$ is equal to the real GDP, as well as aggregate consumption $C_t$ in the equilibrium.
Since consumers only consume final goods and do not directly consume intermediate goods or energy, CPI inflation is determined solely by the price level of final goods:\footnote{For this reason, I hereafter drop the superscript $D$ to emphasise the dynamics of the entire economy, while keep it for describing the downstream industry specifically, but they are the same.}
\begin{equation}
  \pi_t = \pi^D_t = \frac{P^D_t - P^D_{t-1}}{P^D_{t-1}}.
\end{equation}

\subsection{Market Clearing and Aggregation}
Let $Z_t$ denote the aggregate demand for energy by the downstream industry and $N^D_t$ and $N^U_t$ denote the aggregate demand for labour by the downstream and upstream industry, respectively:
\begin{equation}
  Z_t = \int_0^1 Z_t(j) dj, \quad N^D_t = \int_0^1 N^D_t(i) di, \quad N^U_t = \int_0^1 N^U_t(j) dj.
\end{equation}
Then, the total demand for labour in the economy $L_t$ is the sum of the labour demand by the two industries as well as the competitive firms producing the tradable goods:
\begin{equation}\label{eq:labour_demand}
  L_t = N^D_t + N^U_t + E_t.
\end{equation}
By substituting the demand functions for intermediate (\ref{eq:demand_intermediate}) and final goods (\ref{eq:demand_final}), one can obtain the aggregate demands for the intermediate goods $M_t$ and labour $N^D_t$ for the downstream industry and energy $Z_t$ and labour $N^U_t$ for the upstream industry: \textcolor{blue}{MAYBE MOVE THE INTERIM DERIVATIONS TO THE APPENDIX?}
\begin{align}
  M_t &= \int_0^1M_t(i)di = \int_0^1\alpha^DY_t(i)di = \alpha^D\int_0^1\left(\frac{P^D_t(i)}{P^D_t}\right)^{-\varepsilon}Y_tdi \\
      &= \alpha^D\Delta^D_tY_t \\
  N^D_t &= \int_0^1N^D_t(i)di = \int_0^1(1 - \alpha^D)Y_t(i)di = (1 - \alpha^D)\int_0^1\left(\frac{P^D_t(i)}{P^D_t}\right)^{-\varepsilon}Y_tdi \\
        &= (1 - \alpha^D)\Delta^D_tY_t \\
  Z_t &= \int_0^1Z_t(j)dj = \int_0^1\alpha^UQ_t(j)dj = \alpha^U\int_0^1\left(\frac{P^U_t(j)}{P^U_t}\right)^{-\varepsilon}Q_tdj \\
      &= \alpha^U\Delta^U_tQ_t \\
  N^U_t &= \int_0^1N^U_t(j)dj = \int_0^1(1 - \alpha^U)Q_t(j)dj = (1 - \alpha^U)\int_0^1\left(\frac{P^U_t(j)}{P^U_t}\right)^{-\varepsilon}Q_tdj \\
        &= (1 - \alpha^U)\Delta^U_tQ_t,
\end{align}
where $\Delta^D_t = \int_0^1\left(P^D_t(i) / P^D_t\right)^{-\varepsilon} di$ and $\Delta^U_t = \int_0^1\left(P^U_t(j) / P^U_t\right)^{-\varepsilon} dj$ are the usual price dispersion terms for the downstream and upstream industry, respectively.
Substituting the balance of payments condition (\ref{eq:balance_of_payments}) into the labour demand equation (\ref{eq:labour_demand}) gives $L_t = N^D_t + N^U_t + s_tZ_t$.
Further substituting the aggregate demands derived above yields:
\begin{align}
  L_t &= N^D_t + N^U_t + s_tZ_t \\
      &= (1 - \alpha^D)\Delta^D_tY_t + (1 - \alpha^U)\Delta^U_tQ_t + s_t\alpha^U\Delta^U_tQ_t \\
      &= (1 - \alpha^D)\Delta^D_tY_t + (1 - \alpha^U)\Delta^U_tQ_t + \alpha^Us_t\Delta^U_tQ_t \\
      &= (1 - \alpha^D)\Delta^D_tY_t + (1 - \alpha^U + \alpha^Us_t)\Delta^U_t\alpha^D\Delta^D_tY_t \\
      &= [1 - \alpha^D + (1 - \alpha^U + \alpha^Us_t)\alpha^D\Delta^U_t]\Delta^D_tY_t,
\end{align}
which can be rearranged to express the aggregate output $Y_t$ as a function of the total labour demand $L_t$ and the terms of trade $s_t$:
\begin{equation}
  Y_t = \frac{L_t}{[1 - \alpha^D + (1 - \alpha^U + \alpha^Us_t)\alpha^D\Delta^U_t]\Delta^D_t}.
\end{equation}
This implies that the economy's effective labour productivity is
\begin{equation}
  \frac{Y_t}{L_t} = \frac{1}{[1 - \alpha^D + (1 - \alpha^U + \alpha^Us_t)\alpha^D\Delta^U_t]\Delta^D_t},
\end{equation}
which declines as either or both of the industry-wise relative-price distortions $\Delta^D_t$ and $\Delta^U_t$ increase, and as the terms of trade $s_t$ depreciates (i.e., imported energy price increases in domestic currency).
Mathematically, the relative-price distortion in final goods $\Delta^D_t$ has a larger negative effect on the economy's effective labour productivity than that in intermediate goods $\Delta^U_t$, which is intuitive because the former directly affects the price of final goods, while the latter only indirectly affects it through the cost of intermediate goods.
When the terms of trade $s_t$ depreciates, this means that the relative price of energy imports increases compared to other traded goods, which will require more labour input to produce the tradable goods $E_t$ to maintain the balance of payments equilibrium.
Consequently, given the fixed amount of total labour in the economy $L_t$, less labour can be allocated to the production of intermediate and final consumption goods, which is equivalent to a decline in the economy's effective labour productivity. \textcolor{blue}{WHY NEED TO EXPLAIN THIS?}

\subsection{Households and Labour Supply}
As per the standard New Keynesian framework, households with CRRA utility from consumption and disutility from labour supply maximise the expected discounted sum of utility subject to the budget constraint:
\begin{align}
  \max_{\{C_t, B_t, L_t\}_{t = 0}^\infty}\E_0\suminf{t}\beta^t\left[\frac{C_t^{1 - 1/\sigma}}{1 - 1/\sigma} - \frac{L_t^{1 + 1/\psi}}{1 + 1/\psi}\right] \\
  \text{s.t. } P^D_tC_t + B_t = (1 + i_{t-1})B_{t-1} + W_tL_t + \Pi_t,
\end{align}
where $\beta$, $\sigma$, and $\psi$ are the parameters of discount factor, elasticity of intertemporal substitution, and Frisch elasticity of labour supply, respectively, while $B_t$ is the holding of nominal one-period bond, $i_t$ is the nominal interest rate, and $\Pi_t$ is the nominal profit from owning firms.
FOCs with respect to $C_t$ and $L_t$ yield the Euler equation and the labour supply equation, respectively:
\begin{align}
  \frac{C_t^{-1/\sigma}}{P^D_t} &= \beta(1 + i_t)\E_t\left[\frac{C_{t+1}^{-1/\sigma}}{P^D_{t+1}}\right] \label{eq:euler} \\
  \frac{L_t^{1/\psi}}{C_t^{-1/\sigma}} &= \frac{W_t}{P^D_t} = w_t. \label{eq:labour_supply}
\end{align}
\textcolor{blue}{ADD INTUITION FOR EULER EQN?}
The labour supply equation (\ref{eq:labour_supply}) implies that the real wage $w_t$ equals the marginal rate of substitution between consumption and leisure when there is no friction in the labour market.
The following subsection introduces real wage rigidity, however, which potentially generates a wedge between the real wage and the marginal rate of substitution.

\subsection{Real Wage Rigidity}
I introduce real wage rigidity in the labour market, which prevents the real wage from adjusting immediately to the labour market conditions.
Mathematically, following \cite{blanchard2007real}, I assume that the actual real wage $w_t$ is a weighted geometric mean of the lagged real wage $w_{t-1}$ and the flexible real wage $w^f_t$:
\begin{equation}\label{eq:real_wage_process}
  w_t = w_{t-1}^{\psi_w}\cdot (w^f_t)^{1 - \psi_w},
\end{equation}
where $\psi_w \in [0, 1]$ is the parameter that governs the degree of real wage rigidity with $\psi_w = 0$ corresponding to the perfectly flexible labour market with no real wage rigidity.

The real wage rigidity reflects the friction in the labour market, such as fixed contracts, negotiation costs, and separation and hiring costs.\footnote{Though out of scope of the paper, microfoundation can be provided by, for example, introducing search and matching mechanism with Nash bargaining wage negotiation as discussed by \cite{hall2005employment}.}

\subsection{Calvo and Myopic Price Setting}
Both upstream and downstream firms adjust their individual nominal prices $P^U_t(j)$ and $P^D_t(i)$ according to the Calvo pricing model with probability $\theta_U$ and $\theta_D$ of no adjustment, respectively.
The upstream industry firms determine their reset price $P^{U*}_t$ by solving the standard expected discounted profit maximisation problem:
\begin{equation}
  \max_{P^{U*}_t}\E_t\suminf{\ell}(\theta^U)^\ell q_{t+\ell|t}\left[\left(\frac{P^{U*}_t}{P^U_{t+\ell}}\right)^{1 - \varepsilon} - x^U_{t+\ell}\left(\frac{P^{U*}_t}{P^U_{t+\ell}}\right)^{-\varepsilon}\right]Q_{t+\ell}
\end{equation}
where $q_t = Q_tP^D_{t+1}/P^D_t, q_{t+\ell|t} \equiv q_t\cdots q_{t+\ell-1}$ is the real discounted factor.\footnote{As a feature of Leontief production function, the marginal cost does not depend on the firm's own output, so the amount of produced intermediate goods $Q_{t+\ell}$ appears linearly in the objective function.}
Take the FOC with respect to $P^{U*}_t$:
\begin{equation}
  \E_t \suminf{\ell} (\theta^U)^\ell q_{t+\ell|t} \left[(1-\varepsilon) \left( \frac{P^{U*}_t}{P^U_{t+\ell}} \right)^{-\varepsilon} + \varepsilon x^U_{t+\ell} \left( \frac{P^{U*}_t}{P^U_{t+\ell}} \right)^{-\varepsilon-1}\right] \frac{Q_{t+\ell}}{P^U_{t+\ell}} = 0,
\end{equation}
which can be arranged as
\begin{equation}
  P^{U*}_t = \frac{\varepsilon}{\varepsilon-1} \cdot \frac{\E_t \suminf{\ell} (\theta^U)^\ell q_{t+\ell|t} x^U_{t+\ell} (P^U_{t+\ell})^{\varepsilon} Q_{t+\ell}}{\E_t \suminf{\ell} (\theta^U)^\ell q_{t+\ell|t} (P^U_{t+\ell})^{\varepsilon-1} Q_{t+\ell}}.
\end{equation}
In words, the optimal reset price for the intermediate good is a markup over a weighted average of the expected future real marginal cost, where the weights are determined by the Calvo parameter $\theta^U$, the real discount factor $q_{t+\ell|t}$, and the future output $Q_{t+\ell}$. \textcolor{blue}{ADD INTUITION?}
It follows that the upstream industry price level $P^U_t$ is a weighted average of the lagged price level $P^U_{t-1}$ and the reset price $P^{U*}_t$:
\begin{equation}
  P^U_t = [\theta^U P^U_{t-1} + (1 - \theta^U)P^{U*}_t]^\frac{1}{1 - \varepsilon}.
\end{equation}

The downstream industry firms also adopt the same Calvo pricing model with a parameter $\theta^D$ for the probability of no price adjustment.
Additionally, I allow deviations from rational expectations \`a la \cite{gabaix2020behavioral} and \cite{minton2023delayed}; the downstream firms are ``myopic'' in a sense that they discount the future expected marginal cost when setting their reset price, and hence put more weight on the current marginal cost than non-myopic firms do.
To implement myopia, I simply replace the (rational) expectation operator $\E_t[\cdot]$ in the downstream firms' reset price setting problem with a \textit{myopic expectation operator} $\tilde\E[\cdot]$ whose definition is given in the following subsection (since it is defined in terms of the log-deviation of variables from steady state):
\begin{equation}
  \max_{P^{D*}_t} \tilde\E_t \suminf{\ell} (\theta^D)^\ell q_{t+\ell|t} \left[ \left( \frac{P^{D*}_t}{P^D_{t+\ell}} \right)^{1-\varepsilon} - x^D_{t+\ell} \left( \frac{P^{D*}_t}{P^D_{t+\ell}} \right)^{-\varepsilon} \right] \frac{Y_{t+\ell}}{P^D_{t+\ell}}.
\end{equation}
Except for the myopia, the FOC and the optimal reset price for the downstream industry are derived in the same way as the upstream industry.

\subsection{Competitive Equilibrium}
The model is closed by specifying a Taylor monetary policy rule, which I describe in the next subsection in the log-linearised form.
Here, I formally define the competitive equilibrium of the model.
\begin{definition*}[Competitive Equilibrium]
A competitive equilibrium consists of prices $\{P^D_t(i), P^U_t(j), W_t, i_t\}_{t=0}^\infty$ and allocations $\{C_t, Y_t(i), Q_t(j), L_t, N^D_t(i), N^U_t(j), Z_t, E_t, B_t\}_{t=0}^\infty$ such that:
\begin{enumerate}
  \item Households maximise utility with respect to consumption and bond holdings (i.e., the Euler equation (\ref{eq:euler}) holds), while the real wage follows the partial adjustment process (\ref{eq:real_wage_process}), therefore employment is determined by firms' labour demand at the prevailing real wage $w_t$.
  \item The upstream industry firms set prices optimally under Calvo with parameter $\theta^U$, whereas the downstream industry firms set prices optimally under Calvo with parameter $\theta^D$ and myopic expectations.
  \item The labour market clears at the nominal wage $W_t$ with aggregate labour supply $L_t = N^D_t + N^U_t + E_t$.
  \item The intermediate goods market clears in aggregate $Q_t = M_t$, where $Q_t$ is aggregate upstream output and $M_t = \alpha^D\Delta^D_tY_t$ is aggregate demand for intermediate goods composite by the downstream industry.
  \item The consumption goods market clears: $Y_t = C_t$.
  \item The balance of payments equilibrium holds: $E_t = s_tZ_t$.
  \item The bond market clears: $B_t = 0$.
  \item The terms of trade $s_t$ follows the exogenous AR(1) process (\ref{eq:tot_process}).
\end{enumerate}
\end{definition*}

\textcolor{blue}{Model ignores changes in TFP either exogenous or endogenous by the energy price shock.}

\subsection{Log-linearisation}
In this subsection, I log-linearise the model around the steady state. Detailed derivation is provided in Appendix \ref{sec:appendix-derivation}.
\textcolor{blue}{14 endogenous variables and 14 equations.}

First, I define the myopic expectation operator $\tilde\E_t[\cdot]$ for the downstream firms's price setting problem.
\begin{definition*}[Myopic Expectation]
  Let $\hat v_t$ be the log-deviation of a variable $v_t$ from its steady state value $\bar v$, i.e., $\hat v_t = \log(v_t / \bar v)$.
  The myopic expectation of $\hat v_{t+k}$ for $k \geq 0$, denoted by $\tilde\E_t[\hat v_{t+k}]$, is defined as
  \begin{equation}
    \tilde\E_t[\hat v_{t+k}] = m_f^k\E_t[\hat v_{t+k}],
  \end{equation}
  where $m_f \in [0, 1]$ is the myopia parameter with $m_f = 1$ corresponding to the rational expectation case with no myopia, while $m_f = 0$ corresponding to the fully myopic case with no foresight at all.
\end{definition*}

Second, the model requires a monetary policy rule to be closed.
I use a standard log-linearised Taylor rule
\begin{equation}
  \hat i_t = \phi\hat i_{t-1} + (1 - \phi)(\chi_\pi\hat\pi_t + \chi_y\hat y_t)
\end{equation}
with parameters $\phi, \chi_\pi$, and $\chi_y$.

Combined with the log-linearised Taylor rule and the exogenous AR(1) process for the terms of trade (\ref{eq:tot_process}), the following equations complete the log-linearisation of the model:
\begin{align}
  \hat{y}_t &= \hat{L}_t - \alpha^U \alpha^D \hat{s}_t && \text{(aggregate production function)} \label{eq:ll_prod} \\
  \hat{x}^D_t &= \Phi_{DU}(\hat{p}^U_t - \hat{p}^D_t) + (1-\Phi_{DU})\hat{w}_t && \text{(downstream real marginal cost)} \label{eq:ll_rmcD} \\
  \hat{X}^D_t &= \hat{x}^D_t + \hat{p}^D_t && \text{(downstream nominal marginal cost)} \label{eq:ll_nmcD} \\
  \hat{X}^U_t &= \alpha^U \hat{s}_t + \hat{w}_t + \hat{p}^D_t && \text{(upstream nominal marginal cost)} \label{eq:ll_nmcU} \\
  \hat w^f_t &= \frac{1}{\sigma}\hat y_t + \frac{1}{\psi}\hat{L}_t && \text{(flexible real wage)} \label{eq:ll_flexible_wage} \\
  \hat{w}_t &= \psi_w \hat{w}_{t-1} + (1-\psi_w)\hat w^f_t && \text{(real wage rigidity)} \label{eq:ll_rwr} \\
  \hat{\pi}_t &= \hat{p}^D_t - \hat{p}^D_{t-1} && \text{(CPI inflation)} \label{eq:ll_infl} \\
  \hat{p}^D_t &= \theta^D \hat{p}^D_{t-1} + (1-\theta^D)\hat{p}^{D*}_t && \text{(downstream Calvo price level)} \label{eq:ll_calvoD} \\
  \hat{p}^{D*}_t &= \beta m_f \theta^D \E_t[\hat{p}^{D*}_{t+1}] + (1-\beta m_f \theta^D)\hat{X}^D_t && \text{(downstream reset price)} \label{eq:ll_resetD} \\
  \hat{p}^U_t &= \theta^U \hat{p}^U_{t-1} + (1-\theta^U)\hat{p}^{U*}_t && \text{(upstream Calvo price level)} \label{eq:ll_calvoU} \\
  \hat{p}^{U*}_t &= \beta \theta^U \E_t[\hat{p}^{U*}_{t+1}] + (1-\beta\theta^U)\hat{X}^U_t && \text{(upstream reset price)} \label{eq:ll_resetU} \\
  \hat{y}_t &= \E_t[\hat{y}_{t+1}] - \sigma(\hat{i}_t - \E_t[\hat{\pi}_{t+1}]). && \text{(IS equation)} \label{eq:ll_IS}
\end{align}

Here, I derive the log-linearised equation for the downstream real marginal cost (\ref{eq:ll_rmcD}).
Before log-linearisation, the downstream real marginal cost is given by
\begin{equation}
  x^D_t = \left(1 - \alpha^D + \alpha^D\frac{P^U_t}{W_t}\right)w_t. \tag{\ref{eq:rmcD}}
\end{equation}
In the steady state, the nominal marginal cost of the upstream industry is $\bar X^U = \bar W$ from (\ref{eq:nmcU}).
Also, every firm in the upstream industry will set the optimal reset price, which is the steady state nominal marginal cost multiplied by the constant markup:
\begin{equation}
  \bar P^U = \mu \bar W = \frac{\varepsilon}{\varepsilon - 1} \bar W,
\end{equation}
where $\mu \equiv \varepsilon / (\varepsilon - 1)$ is the markup.
It follows that the steady state real marginal cost of the downstream industry is
\begin{equation}
  \bar x^D = (1 - \alpha^D + \alpha^D\mu)\bar w.
\end{equation}
The log deviation of $P^U_t / W_t$ is $\hat P^U_t - \hat W_t$, and since $w_t = W_t / P^D_t$, $\hat W_t = \hat w_t + \hat p^D_t$.
Therefore,
\begin{equation}
  \widehat{\left(\frac{P^U_t}{W_t}\right)} = \hat p^U_t - \hat w_t - \hat p^D_t.
\end{equation}
Log-linearising $x^D_t$ around the steady state gives
\begin{align}
  \hat x^D_t &= \frac{\alpha^D\cdot \bar P^U / \bar W}{1 - \alpha^D + \alpha^D\cdot \bar P^U / \bar W}(\hat p^U_t - \hat w_t - \hat p^D_t) + \hat w_t \\
             &= \frac{\alpha^D\mu}{1 - \alpha^D + \alpha^D\mu}(\hat p^U_t - \hat w_t - \hat p^D_t) + \hat w_t &\text{since $\mu = \bar P^U / \bar W$} \\
             &= \Phi_{DU}(\hat p^U_t - \hat w_t - \hat p^D_t) + \hat w_t, \\
             &= \Phi_{DU}(\hat p^U_t - \hat p^D_t) + (1 - \Phi_{DU})\hat w_t,
\end{align}
where
\begin{equation}
  \Phi_{DU} = \frac{\alpha^D\mu}{1 - \alpha^D + \alpha^D\mu}.
\end{equation}

\subsection{Calibration}
I calibrate the model based on the UK economy around the 2022 Energy Crisis.
The model period is monthly.
Summary of the parameter values is presented in Table \ref{tab:parameters}.
Here, I describe the sources and rationales of the calibration choices for each parameter.

First, the three parameters in the households' utility function follow the standard in the New Keynesian Literature: the discount factor $\beta$ is set to 0.9984, implied by the annual real interest rate of 2\%; elasticity of intertemporal substitution $\sigma$ is set to 0.5; and the Frisch elasticity of labour supply $\psi$ is set to 3.

In the production network, I set the elasticity of substitution $\varepsilon$ to 11, which implies the standard New Keynesian steady state markup of $\mu = 1.1$.
% As discussed in the model section, I assume that the elasticity of substitution and subsequently the markup are the same for both upstream and downstream industry.
Meanwhile, I set the energy cost share in the upstream industry $\alpha^U$ to 0.375.
The upstream industry in the model represents energy-intensive sectors that utilise imported energy as input to produce intermediate goods.
Using the annual Supply and Use Tables from the ONS, I calculated the output-weighted average energy cost share across the eight most energy-intensive and intermediate-goods-producing sectors annually from 2017 to 2022.\footnote{Specifically, the eight sectors are Electric Power Generation (\texttt{CPA\_D351}), Gas Manufacture \& Distribution (\texttt{CPA\_D352\_3}), Industrial Gases, Inorganics, Fertilisers (\texttt{CPA\_C20A}), Petrochemicals (\texttt{CPA\_C20B}), Paper and Paper Products (\texttt{CPA\_C17}), Glass, Ceramics, Stone (\texttt{CPA\_C23OTHER}), Basic Iron and Steel (\texttt{CPA\_C241\_3}), and Other Basic Metals \& Casting (\texttt{CPA\_C244\_5}). Detailed calculations are available in Appendix \ref{sec:appendix-calculations}. \textcolor{blue}{Limitation: those industries also produce final goods.}}
I adopt the average of the annual figures for 2017-2019 as the steady state value for $\alpha^U = 0.375.$
$\alpha^D$ indicates the intermediate input share in the downstream industry, which is set to be 0.4.
This implies that the overall energy cost share in the final consumption goods is $\alpha^U\alpha^D = 0.15$.
$\Phi_{DU}$ is derived as
\begin{equation}
  \Phi_{DU} = \frac{\alpha^D\mu}{1 - \alpha^D + \alpha^D\mu} = 0.4231,
\end{equation}
which is the cost-based share of the intermediate goods in the downstream industry's real marginal cost.
The difference to $\alpha^D$ is that the upstream industry's markup on the intermediate goods is taken into account in $\Phi_{DU}$.


\begin{table}[htbp]
  \centering
  \caption{Model Parameter Values \textcolor{blue}{Remove source/rationale column?}}
  \label{tab:parameters}
  \begin{tabular}{llrl}
    \toprule
    Parameter & Symbol & Value & Source / Rationale \\
    \midrule
    \multicolumn{4}{l}{\textit{Households}} \\
    Discount factor & $\beta$ & 0.9984 & Implied by $\bar{r} = 2\%$ annual, monthly \\
    Elasticity of intertemporal substitution & $\sigma$ & 0.5 & Standard NK \\
    Frisch elasticity of labour supply & $\psi$ & 3 & Standard macro estimate \\
    \addlinespace[0.4em]
    \multicolumn{4}{l}{\textit{Production and cost structure}} \\
    Energy cost share (upstream) & $\alpha^U$ & 0.375 & Energy-intensive upstream sector \\
    Intermediate input share (downstream) & $\alpha^D$ & 0.4 & $\alpha^U \alpha^D \approx$ baseline \textcolor{blue}{FIXME:}\\
    Elasticity of substitution & $\varepsilon$ & 11 & Markup $\mu = 1.1$; standard NK \\
    Downstream upstream-cost share & $\Phi_{DU}$ & 0.4231 & Derived: $\Phi_{DU} = \alpha^D \mu / (1 - \alpha^D + \alpha^D \mu)$ \\
    \addlinespace[0.4em]
    \multicolumn{4}{l}{\textit{Price setting}} \\
    Downstream Calvo probability & $\theta^D$ & 11/12 & Avg.\ duration 12 months \\
    Upstream Calvo probability & $\theta^U$ & 3/4 & Avg.\ duration 4 months; N\&S (2008) \\
    Myopia parameter (downstream) & $m_f$ & 0.25 & Gabaix (2020), M\&W (2023) \\
    \addlinespace[0.4em]
    \multicolumn{4}{l}{\textit{Labour market}} \\
    Real wage rigidity & $\psi_w$ & 0.705 & G\&G (2025); B\&G (2007) range \\
    \addlinespace[0.4em]
    \multicolumn{4}{l}{\textit{Monetary policy}} \\
    Interest-rate smoothing & $\phi$ & 0.9 & Consistent with BoE behaviour \\
    Inflation response & $\chi_\pi$ & 3 & Satisfies Taylor principle \\
    Output response & $\chi_y$ & 0.5 & Standard Taylor rule \\
    \addlinespace[0.4em]
    \multicolumn{4}{l}{\textit{Shock process}} \\
    Terms of trade persistence & $\rho$ & 0.8 & \\
    \bottomrule
  \end{tabular}
\end{table}


\textcolor{blue}{\url{https://www.ons.gov.uk/economy/nationalaccounts/supplyandusetables/datasets/ukinputoutputanalyticaltablesdetailed} UK input-output tables, potentially useful to calibrate $\alpha^U$ and $\alpha^D$.}

\section{Results and Discussion}\label{sec:results_and_discussion}

\subsection{Sensitivity Analysis}\label{subsec:sensitivity_analysis}

Sensitivity analysis:
\begin{easylist}[itemize]
\ListProperties(Style=\color{blue})
  @ Varying the degree of real wage rigidity $\psi_w \in \{0.705\}$
  @ upstream Calvo pricing parameter $\theta_U \in \{0.5\} + \{0, 0.3, 0.7\}$ \citep{nakamura2008five}
  @ Downstream myopica parameter $m_f \in \{0, 0.5, 1\}$
  @ CES rather than Leontief production function?
  @ Values of $\alpha$'s
\end{easylist}

\section{Conclusion}\label{sec:conclusion}

Model limitations:
\begin{easylist}[itemize]
\ListProperties(Style=\color{blue})
  @ Network structure of production and input-output linkages
\end{easylist}

% \newpage
\bibliographystyle{econ-aea}
\bibliography{bibliography}

\appendix
\section{Appendix: Derivation of Log-linearised Equations}\label{sec:appendix-derivation}
\section{Appendix: Calculations}\label{sec:appendix-calculations}
\textcolor{blue}{Table? and graph for estimating $\alpha^U$}

\end{document}