---
title: "Untitled"
author: Shunsuke Ishii
editor:
  render-on-save: false
format: html
jupyter: r
lang: en-GB
---

::: {.hidden}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\inR}{\in \mathbb{R}}
\newcommand{\inN}{\in \mathbb{N}}
\newcommand{\inZ}{\in \mathbb{Z}}
\newcommand{\inQ}{\in \mathbb{Q}}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\tand}{\text{ and }}
\newcommand{\tor}{\text{ or }}
\newcommand{\se}{\text{se}}
\newcommand{\Var}{\text{Var}}

\newcommand{\suminf}[1]{\sum_{#1=0}^\infty}
\newcommand{\sumin}{\sum_{i=1}^n}
:::


```{r}
library(tidyverse)
library(fredr)
library(estatapi)
library(gridExtra)
library(forecast)
```


```{r}
FRED_API_KEY <- scan("fred_APIkey.txt", what = "character")
fredr_set_key(FRED_API_KEY)

appId <- scan("e-stat_appId.txt", what = "character")
```


```{r}
# Consumer Price Indices (CPIs, HICPs), COICOP 1999: Consumer Price Index: Total for United Kingdom
# Units: Contribution to growth rate, over 1 year, Not Seasonally Adjusted
# Frequency: Monthly
GBRCPALTT01CTGYM <- fredr(
  series_id = "GBRCPALTT01CTGYM",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31")
)

# Crude Oil Prices: Brent - Europe
# Units: Dollars per Barrel, Not Seasonally Adjusted
# Frequency: Daily

DCOILBRENTEU <- fredr(
  series_id = "DCOILBRENTEU",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31"),
  frequency = "m"
)

# Global price of Natural gas, EU
# Units: U.S. Dollars per Million Metric British Thermal Unit, Not Seasonally Adjusted
# Frequency: Monthly
PNGASEUUSDM <- fredr(
  series_id = "PNGASEUUSDM",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31"),
  frequency = "m"
)
```


```{r}
crude_oil <- DCOILBRENTEU %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(crude_oil_price = value)
crude_oil_price_201809 <- crude_oil %>%
  filter(date == as.Date("2018-09-01")) %>%
  pull(crude_oil_price)
crude_oil <- crude_oil %>%
  mutate(crude_oil_price_relative = crude_oil_price / crude_oil_price_201809 * 100)

natural_gas <- PNGASEUUSDM %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(natural_gas_price = value)
natural_gas_price_201809 <- natural_gas %>%
  filter(date == as.Date("2018-09-01")) %>%
  pull(natural_gas_price)
natural_gas <- natural_gas %>%
  mutate(natural_gas_price_relative = natural_gas_price / natural_gas_price_201809 * 100)
```

```{r}
natural_gas_arima <- auto.arima(natural_gas$natural_gas_price)
summary(natural_gas_arima)
pacf(natural_gas_arima$residuals)
```

```{r}
inner_join(crude_oil, natural_gas) %>%
  select(-crude_oil_price, -natural_gas_price) %>%
  pivot_longer(cols = c(crude_oil_price_relative, natural_gas_price_relative),
         names_to = "type",
         values_to = "price_relative") %>% filter(date >= ym(201809)) %>%
    ggplot(aes(x = date, y = price_relative, color = type)) +
    geom_line() +
    labs(x = "Date", y = "Relative Price (Sep 2018 = 100)", color = "Type") +
    scale_color_hue(name = "", labels = c("Crude Oil", "Natural Gas")) +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    theme_minimal() -> p1
ggsave("crude_oil_natural_gas_prices.pdf")
```

```{r}
cpi_uk <- GBRCPALTT01CTGYM %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(cpi_uk = value)
```

```{r}
# estat_getMetaInfo(appId = appId, statsDataId = "0003427113")
cpi_japan <- estat_getStatsData(
  appId = appId,
  statsDataId = "0003427113",
  lang = "E",
  cdTab = "3",
  lvTime = "4",
  cdTimeFrom = "20100000101",
  cdTimeTo = "2025000303",
  cdArea = "00000",
  cdCat01 = "0001"
)
```

```{r}
cpi_japan <- cpi_japan %>%
  mutate(date = my(Time)) %>%
  rename(cpi_japan = value) %>%
  select(date, cpi_japan)
```

```{r}
# Consumer Price Indices (CPIs, HICPs), COICOP 1999: Consumer Price Index: Total for Germany
# Units: Growth rate same period previous year, Not Seasonally Adjusted
# Frequency: Monthly
CPALTT01DEM659N <- fredr(
  series_id = "CPALTT01DEM659N",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31")
)

cpi_de <- CPALTT01DEM659N %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(cpi_de = value)
```

```{r}
inner_join(cpi_uk, cpi_japan) %>%
  inner_join(cpi_de) %>%
  pivot_longer(cols = c(cpi_uk, cpi_japan, cpi_de),
         names_to = "country",
         values_to = "cpi") %>% filter(date >= ym(201809)) %>%
    ggplot(aes(x = date, y = cpi, color = country)) +
    geom_line() +
    labs(x = "Date", y = "CPI Inflation", color = "country") +
    scale_color_hue(name = "", labels = c("Germany", "Japan", "UK")) +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    theme_minimal() -> p2
ggsave("cpi_inflation.pdf")
```

```{r}
grid.arrange(p1, p2, nrow = 2)
```