---
title: "Untitled"
author: Shunsuke Ishii
editor:
  render-on-save: false
format: html
jupyter: r
lang: en-GB
---

::: {.hidden}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\inR}{\in \mathbb{R}}
\newcommand{\inN}{\in \mathbb{N}}
\newcommand{\inZ}{\in \mathbb{Z}}
\newcommand{\inQ}{\in \mathbb{Q}}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\tand}{\text{ and }}
\newcommand{\tor}{\text{ or }}
\newcommand{\se}{\text{se}}
\newcommand{\Var}{\text{Var}}

\newcommand{\suminf}[1]{\sum_{#1=0}^\infty}
\newcommand{\sumin}{\sum_{i=1}^n}
:::


```{r}
library(tidyverse)
library(ggh4x)
library(fredr)
```

```{r}
FRED_API_KEY <- scan("fred_APIkey.txt", what = "character")
fredr_set_key(FRED_API_KEY)
```


```{r}
# Consumer Price Indices (CPIs, HICPs), COICOP 1999: Consumer Price Index: Total for United Kingdom
# Units: Contribution to growth rate, over 1 year, Not Seasonally Adjusted
# Frequency: Monthly
GBRCPALTT01CTGYM <- fredr(
  series_id = "GBRCPALTT01CTGYM",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31")
)

CPGRLE01GBM659N <- fredr(
  series_id = "CPGRLE01GBM659N",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31")
)

# Crude Oil Prices: Brent - Europe
# Units: Dollars per Barrel, Not Seasonally Adjusted
# Frequency: Daily
DCOILBRENTEU <- fredr(
  series_id = "DCOILBRENTEU",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31"),
  frequency = "m"
)

# Global price of Natural gas, EU
# Units: U.S. Dollars per Million Metric British Thermal Unit, Not Seasonally Adjusted
# Frequency: Monthly
PNGASEUUSDM <- fredr(
  series_id = "PNGASEUUSDM",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31"),
  frequency = "m"
)

# U.S. Dollars to U.K. Pound Sterling Spot Exchange Rate
# Units: U.S. Dollars to One U.K. Pound Sterling, Not Seasonally Adjusted
# Frequency: Daily
DEXUSUK <- fredr(
  series_id = "DEXUSUK",
  observation_start = as.Date("2010-01-01"),
  observation_end = as.Date("2025-03-31"),
  frequency = "m"
)

```


```{r}
dollar_pound <- DEXUSUK %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(exchange_rate = value)

crude_oil <- DCOILBRENTEU %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(crude_oil_price = value)

natural_gas <- PNGASEUUSDM %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(natural_gas_price = value)

energy_prices <- dollar_pound %>%
  left_join(crude_oil) %>%
  left_join(natural_gas)

energy_prices <- energy_prices %>%
  mutate(
    crude_oil_price_gbp = crude_oil_price / exchange_rate,
    natural_gas_price_gbp = natural_gas_price / exchange_rate,
  ) %>%
  select(-exchange_rate, -crude_oil_price, -natural_gas_price)

crude_oil_price_201809 <- energy_prices %>%
  filter(date == as.Date("2018-09-01")) %>%
  pull(crude_oil_price_gbp)
natural_gas_price_201809 <- energy_prices %>%
  filter(date == as.Date("2018-09-01")) %>%
  pull(natural_gas_price_gbp)

energy_prices <- energy_prices %>%
  mutate(
    crude_oil_price_relative = crude_oil_price_gbp / crude_oil_price_201809 * 100,
    natural_gas_price_relative = natural_gas_price_gbp / natural_gas_price_201809 * 100
  )
```

```{r}
energy_prices %>%
  pivot_longer(
    cols = c(crude_oil_price_relative, natural_gas_price_relative),
    names_to = "type",
    values_to = "price_relative"
  ) %>%
  filter(date >= ym(201809)) %>%
  ggplot(aes(x = date, y = price_relative, color = type)) +
  geom_line() +
  geom_hline(yintercept = 100, linetype = "dashed") +
  labs(x = "Date", y = "Relative Price (Sep 2018 = 100)", color = "Type") +
  scale_color_hue(name = "", labels = c("Crude Oil", "Natural Gas")) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_bw()
```

```{r}
cpi <- GBRCPALTT01CTGYM %>%
  select(-realtime_start, -realtime_end, -series_id) %>%
  rename(cpi = value)

# cpi_core <- CPGRLE01GBM659N %>%
#   select(-realtime_start, -realtime_end, -series_id) %>%
#   rename(cpi_core = value)
```

```{r}
scale_factor <- 800 / 12  # left axis max / right axis max

plot_data <- energy_prices %>%
  filter(date >= ym(201809)) %>%
  left_join(cpi)

plot_data %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = natural_gas_price_relative, color = "Natural Gas", linetype = "Natural Gas")) +
  geom_line(aes(y = crude_oil_price_relative, color = "Crude Oil", linetype = "Crude Oil")) +
  geom_line(
    aes(y = cpi * scale_factor, color = "CPI Inflation", linetype = "CPI Inflation"),
    linewidth = 1.1
  ) +
  # geom_hline(yintercept = 100, linetype = "dotted", alpha = 0.5) +
  scale_y_continuous(
    name = "Relative Price (Sep 2018 = 100)",
    breaks = seq(0, 800, 100),
    sec.axis = sec_axis(~ . / scale_factor, name = "Inflation (% YoY)")
  ) +
  scale_color_manual(
    name = "",
    values = c(
      "Natural Gas" = "#D55E00",
      "Crude Oil" = "#0072B2",
      "CPI Inflation" = "black"
    )
  ) +
  scale_linetype_manual(
    name = "",
    values = c(
      "Natural Gas" = "solid",
      "Crude Oil" = "solid",
      "CPI Inflation" = "dotdash"
    )
  ) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    color = guide_legend(override.aes = list(linewidth = 0.6))
  ) +
  scale_x_date(
    date_breaks = "1 year",
    minor_breaks = seq(as.Date("2019-01-01"), as.Date("2025-06-01"), by = "6 months"),
    date_labels = "%Y"
  ) +
  labs(x = "Date") +
  theme_classic() +
  theme(legend.position = "bottom")
ggsave("figure/energy_prices_cpi_inflation.png", width = 8, height = 6, dpi = 300)
```

# Note: Core CPI
Core CPI inflation remained high, or even higher than CPI inflation after 2023.
This implies second-round effects of energy price shock.